NumPy---Array Programming in Python

### 2020-01-16 methods.tex
Fix typo

We use Git for version control and GitHub as the public hosting service for our
official \emph{upstream} repository (\url{https://github.com/numpy/numpy}).
We each work in our own copy (or fork) of the project and use the
upstream repository as our integration point.
To get new code into the upstream repository, we use GitHub's
pull request (PR) mechanism.
This allows us to review code before integrating it as well as to run a
large number of tests on the modificatied code to ensure that it does not
break things.

>>>>

We use Git for version control and GitHub as the public hosting service for our
official \emph{upstream} repository (\url{https://github.com/numpy/numpy}).
We each work in our own copy (or fork) of the project and use the
upstream repository as our integration point.
To get new code into the upstream repository, we use GitHub's
pull request (PR) mechanism.
This allows us to review code before integrating it as well as to run a
large number of tests on the modified code to ensure that it does not
break things.
